\chapter{Conclusions} \label{conclusions}

\section{Final thoughts}

This document was redacted following the guidelines for the project (\textit{eMall - e-Mobility for All project}). Discrepancies between our document and the guidelines are to be considered our hypothesis on how the two systems should behave or be modeled.\medskip

Also, these systems have been designed having in mind possible future expansions. Thus, anyone who wants to expand this project is welcome and encouraged to do so. For example, one possibility is to set a limit after which the user is no more allowed to book charges until s/he decides to pay the previous ones.

\section{Credits}

For writing this document, we used different pieces of software and materials from the Internet. This is a rather comprehensive list of them:
\begin{itemize}
    \item \href{https://www.latex-project.org/}{\textit{\LaTeX} (with packages)} and \href{https://code.visualstudio.com/}{\textit{Visual Studio Code} (with plugins)} for writing the document.
    \item \href{https://git-scm.com/}{\textit{Git}}, \href{https://github.com/}{\textit{GitHub}} and \href{https://www.notion.so/}{\textit{Notion}} for keeping things organized.
    \item \href{https://www.diagrams.net/}{\textit{draw.io}} and \href{https://plantuml.com/}{\textit{PlantUML}} for creating the diagrams.
    \item \href{https://fonts.google.com/icons}{\textit{Google Fonts} (icon library)}, \href{https://inkscape.org/}{\textit{Inkscape}}, \href{https://www.openstreetmap.org/}{\textit{OpenStreetMap}}, \href{https://penpot.app/}{\textit{Penpot}} (with designs from \href{https://ape.wtf/}{ApeWTF} and \href{https://design.google/library/designing-material/}{Google}) and \href{https://www.wikipedia.org/}{\textit{Wikipedia}} for drawing the mockups.
\end{itemize}

\section{Effort}

\begin{center}
    \begin{tabular}{ | >{\arraybackslash}m{0.52\columnwidth} | >{\centering\arraybackslash}m{0.2\columnwidth} | >{\centering\arraybackslash}m{0.2\columnwidth} | }
        \hline
        \multicolumn{1}{|c|}{\textbf{Task}} & \textbf{Riccardo Motta} & \textbf{Pierluigi Negro} \\
        \hline
        \hline
        Writing chapter 1 & 3h & 2h \\
        \hline
        Writing chapter 2 & 4h & 4h \\
        \hline
        Drawing overview, composition diagrams, component views and deployment view & 6h & 7h \\
        \hline
        Drawing runtime views and components interfaces & 4h & 8h \\
        \hline
        Writing chapter 3 & 2h & 1h \\
        \hline
        Designing the mockups & 20h & 18h \\
        \hline
        Creating the pages connections diagrams & 2h & 1h \\
        \hline
        Mapping components and requirements and writing chapter 4 & 2h & 2h \\
        \hline
        Writing chapter 5 & 3h & 1h \\
        \hline
        Other related work & 5h & 4h \\
        \hline
        Updating document for Version 1.1 & 0.5h & 0.5h \\
        \hline
        \hline
        \textbf{Total} & \textbf{51.5h} & \textbf{48.5h} \\
        \hline
    \end{tabular}
\end{center}
